\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{longtable}
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage[big]{layaureo} 				%better formatting of the A4 page
\usepackage{fullpage}
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{enumitem}           % to change itemize margins
\setlist[itemize]{leftmargin=0.25cm}
\usepackage{longtable}			 % for multipage tables
\usepackage[none]{hyphenat} % prevent all hypenation

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge \textsc{Rahul Dhodapkar}
	}\bigskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
\section{Personal}

\begin{tabular}{rl}
    \textsc{Address:}   & 4937 Genevieve Ave., Los Angeles, CA 90041 \\
    \textsc{Telephone:}      & +1 347 563 3757\\
    \textsc{Email:}       & \href{mailto:rahul.dhodapkar@med.usc.edu}{rahul.dhodapkar@med.usc.edu}
\end{tabular}

%Section: Education
\section{Education}
\begin{tabular}{rl}	
 \textsc{May} 2023 & Doctor of Medicine,\
 \textbf{Yale School of Medicine}, New Haven, CT\\
\\
 \textsc{May} 2017 & Non-degree Postbacc,\
 \textbf{New York University}, New York, NY\\
\\
 \textsc{May} 2015 & Bachelor of Science in \
 \textsc{Computer Science}, \textbf{Yale University}, New Haven, CT\\
\\
\textsc{May} 2011 & High School,\
 \normalsize \textbf{Hopkins School}, New Haven, CT\\
\end{tabular}

%Section: Work Experience at the top
\section{Work}
\begin{longtable}{r|p{11cm}}
 \nopagebreak \textsc{Current} & Resident Physician at \textsc{Keck School of Medicine}\\
 \nopagebreak \textsc{June 2023} & \small{Los Angeles, CA, USA} \\
 \nopagebreak & \footnotesize{
	\begin{itemize}
		\item[]{
			Resident physician in ophthalmology at Keck School of Medicine and LA General Medical Center.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Sep 2022} & Neuroinflammation Research Fellow at \textsc{Yale School of Medicine}\\
 \nopagebreak \textsc{Sep 2021} & \small{New Haven, CT, USA} \\
 \nopagebreak & \footnotesize{
	\begin{itemize}
		\item[]{
			Led single-nucleus RNA sequencing project to characterize activated Muller glia in glaucoma and identify potential targets for neuroregnerative therapeutics.
		}
		\item[]{
			Mentored undergraduate and postgraduate students, training them in laboratory techniques as well as scientific knowledge and approach.
		}
		\item[]{
			Contributed to analysis and experimental design for project to characterize microglial involvement in the development of age-related macular degeneration (AMD) and compare it to other neurodegenerative disorders.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2018} & Consulting Engineer at \textsc{MongoDB Inc.}\\
 \nopagebreak \textsc{Aug 2015} & \small{New York, NY, USA} \\
 \nopagebreak & \footnotesize{
	\begin{itemize}
		\item[]{
			Architected and built information management systems for dozens of Fortune 500
			clients, including:
		}
		\item[]{
			A critical resource management system used daily by over 7000 employees of the City of New York.
		}
		\item[]{
			A HIPAA-compliant database to store medical sensor data for thousands of patients
in clinical trials.
		}
		\item[]{
			A globally distributed multi-terabyte database-as-a-service (DaaS) system with
99.999\% uptime guarantee.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Mar 2015} & Consultant at \textsc{Sears Holdings Corporation}\\
 \nopagebreak \textsc{Aug 2014} & \small{Hoffman Estates, IL, USA}\\
 \nopagebreak & \footnotesize{
	\begin{itemize}
		\item[]{
			Standardized external product interfaces for Sears’ integrated home platform.
		}
		\item[]{
			Wrote middleware to unify distributed callback mechanisms for internet of things (IoT) applications.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Jul 2014} & Software Engineering Intern at \textsc{MongoDB Inc.}\\
 \nopagebreak \textsc{May 2014} & \small{New York, NY, USA} \\
 \nopagebreak	& \footnotesize{
	\begin{itemize}
		\item[]{
			Prototyped a new query optimization system for the MongoDB kernel, using
machine learning techniques to reduce execution time.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{July 2013} & Research and Development Intern at \textsc{Epic Systems}\\
 \nopagebreak \textsc{May 2013} & \small{Verona, WI, USA} \\
 \nopagebreak	& \footnotesize{
	\begin{itemize}
		\item[]{
			Led a team of interns in building a web-application for mining patient data across
			hospitals using Epic.
		}
		\item[]{
			Wrote a graph-based clustering algorithm to connect physicians based on
previously seen patient characteristics to promote collaboration in the diagnosis
of ambiguously-presenting patients.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{July 2012} & Software Development Intern at \textsc{VantageLocal}, \small\emph{(now \textsc{Frequence})}\\
 \nopagebreak \textsc{May 2012} & \small{Palo Alto, CA, USA}\\
 \nopagebreak & \footnotesize{
	\begin{itemize}
		\item[]{
			Developed a web application to automate quote generation for
			locally targeted, real time bid (RTB) advertising.
		}
		\item[]{
			Wrote Flash-based tools to assist advertising creative team
			in banner ad design.
		}
	\end{itemize}
   }\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Feb 2012} & Research Associate at \textsc{Yale Child Study Center} \\
 \nopagebreak \textsc{May 2008} & \small\emph{Lab of \textsc{Dr. Matthew State} (now at \textsc{University of California, San Francisco})} \\
 \nopagebreak & \small{New Haven, CT, USA} \\
 \nopagebreak & \footnotesize{
	\begin{itemize}
		\item[]{
			Wrote graphical interface for CNVision, a comprehensive toolkit for copy number
variant (CNV) analysis of genotyping data.
		}
		\item[]{
			Developed custom scripts for data analysis and performed polymerase chain
			reaction (PCR) to generate samples for next-gen genome sequencing and RNA
			extraction for expression profiling of brain tissue.
		}
	\end{itemize}
   }\\
\end{longtable}

%Section: Volunteer work
\section{Service}
\begin{longtable}{r|p{11cm}}
 \nopagebreak \textsc{Jan 2022} & Senior Clinical Team Member at \textsc{HAVEN Free Clinic}\\
 \nopagebreak \textsc{May 2021} &  \small{New Haven, CT, USA}\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2020} & Volunteer at \textsc{YSM Anatomy Teaching Program} \\
 \nopagebreak \textsc{Aug 2018} &  \small{New Haven, CT, USA}\\
 \multicolumn{2}{c}{} \\
  \nopagebreak \textsc{May 2020} & Volunteer at \textsc{Code Haven} \\
 \nopagebreak \textsc{Aug 2018} &  \small{New Haven, CT, USA}\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2018} & Volunteer at \textsc{Mount Sinai Hospital, Ruttenberg Cancer Center} \\
 \nopagebreak \textsc{Aug 2016} &  \small{New York, NY, USA}\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2014} & Philanthropy Chair at \textsc{Sigma Chi Fraternity}\\
 \nopagebreak \textsc{Sep 2014} & \small{New Haven, CT, USA} \\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2013} & Literacy Tutor at \textsc{New Haven Reads}\\
 \nopagebreak \textsc{Sep 2012} & \small{New Haven, CT, USA} \\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Jun 2009} & TA at \textsc{Moving Academy of Medicine and Biomedicine} \\
 \nopagebreak \textsc{May 2009} & \small{Pune, MH, Republic of India} \\
\end{longtable}

%Section: Leadership
\section{Leadership}
\begin{longtable}{r|p{11cm}}
 \nopagebreak \textsc{May 2022} & Director of Medical Debt and Insurance Counseling\\
 \nopagebreak \textsc{May 2021} &  \small{HAVEN Free Clinic}\\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2018} & Cybersecurity Standardization Field Lead \\
 \nopagebreak \textsc{Aug 2016} & \small\emph{MongoDB} \\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{May 2014} & Treasurer and Philanthropy Chair \\
 \nopagebreak \textsc{Aug 2013} & \small\emph{Sigma Chi Fraternity at Yale} \\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Jan 2014} & Director of Technology \\
 \nopagebreak \textsc{Sep 2012} & \small\emph{Yale Event Management Association} \\
 \multicolumn{2}{c}{} \\
 \nopagebreak \textsc{Aug 2013} & Social Chair \\
 \nopagebreak \textsc{Sep 2012} & \small\emph{Yale Equestrian Team} \\
 \multicolumn{2}{c}{} \\
\end{longtable}


%Section: Scholarships and additional info
\section{Funding}
\begin{tabular}{rp{11cm}}
\textsc{Jun} 2024 & Colton Center for Autoimmunity Grant \\
 							    & \textbf{Co-investigator} \\
								& \textit{AI-Simulated In Silico Humans: A New Paradigm for Modeling Autoimmunity}: a \$100,000 grant to develop new therapeutic targets for age-related macular degeneration (AMD) using a novel AI-driven \textit{in silico} human perturbation screening platform.
\end{tabular}

%Section: Scholarships and additional info
\section{Awards and Honors}
\begin{tabular}{rp{11cm}}
\textsc{Dec} 2022 & Yale/Boehringer Ingelheim Datathon Winner \\
 							    & \small\emph{Most outstanding multimodal data integration tool at the Yale/BI Datathon} \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2022 & SAIL Travel Award \\
 							    & \small\emph{Travel award to fund presentation at the Symposium on Artificial Intelligence for Learning Health Systems (SAIL)} \\
 \multicolumn{2}{c}{} \\
 \textsc{Jan} 2022 & Sigma Xi Scientific Research Honor Society \\
 							    & \small\emph{Nominated to full member of Sigma Xi honor society.} \\
 \multicolumn{2}{c}{} \\
 \textsc{June} 2021 & Medical Student Research Award \\
 							    & \small\emph{Yale Ophthalmology department  award for most outstanding medical student research.} \\
 \multicolumn{2}{c}{} \\
 \textsc{Apr} 2020 & Honorable Mention: Marguerite Rush Lerner Contest \\
 							    & \small\emph{Medical student creative writing \& art contest at Yale School of Medicine.} \\
 \multicolumn{2}{c}{} \\
 \textsc{Mar} 2018 & Young Investigator Award \\
 							    & \small\emph{Travel award from Thrombosis and Hemostatsis Societies of North America.} \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2015 & Sigma Chi Chapter Balfour Prize \\
 							    & \small\emph{For most outstanding senior in the graduating class.} \\
 \multicolumn{2}{c}{} \\
 \textsc{Aug} 2013 & Sigma Chi J. Willard Marriott Scholarship \\
 \multicolumn{2}{c}{} \\
 \textsc{Jun} 2013 & ThinkChicago Lollapalooza Winner \\
 							    & \small\emph{Municipal innovation pitch competition by the City of Chicago} \\
 \multicolumn{2}{c}{} \\
 \textsc{Oct} 2012 & Yale Venture Creation Program Fellow \\
 \multicolumn{2}{c}{} \\	
 \textsc{Sep} 2012 & Yale Entrepreneurial Society Elevator Pitch Competition Runner Up \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2011 & New Haven Register Youth of the Year \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2011 & National Merit Scholarship Finalist \\
 \multicolumn{2}{c}{} \\
\end{tabular}

\section{Articles}
Contributions bolded; {\bf *} indicates co-first author, {\bf $\dag$} indicates co-corresponding author. 

\begin{longtable}{rp{11cm}}
\textit{\textsc{In Review}}& \textbf{Rahul M. Dhodapkar}, Eric Jung, Sun Young Lee. {\it An eye on extracellular vesicles: Trends and clinical translations in vision research.}\\
\multicolumn{2}{c}{} \\

\textit{\textsc{In Review}}& \textbf{Rahul M. Dhodapkar,} Sean J. Miller, Abdelilah Majdoubi, Diego Martell, Rayyan Y. Darji, Hande Eda Sutova, Alex Dong, Michael Heyang, Marcello DiStasio, Brian P. Hafler. {\it Single-cell cross-species analysis reveals pathways promoting regeneration in the human retina.}\\
\multicolumn{2}{c}{} \\

\textit{\textsc{In Press}}& Daniel Levine, Sacha Lévy, Syed Asad Rizvi, Nazreen Pallikkavaliyaveetil, Xingyu Chen, David Zhang, Sina Ghadermarzi, Ruiming Wu, Zihe Zheng, Ivan Vrkic, Anna Zhong, Daphne Raskin, Insu Han, Antonio Henrique de Oliveira Fonseca, Josue Ortega Caro, Amin Karbasi, \textbf{Rahul M. Dhodapkar $\dag$}, David van Dijk $\dag$. {\it Cell2Sentence: Teaching Large Language Models the Language of Biology.} Proceedings of the International Conference on Machine Learning. https://doi.org/10.1101/2023.09.11.557287\\
\multicolumn{2}{c}{} \\

\textit{\textsc{In Press}}& Josue Ortega Caro, Antonio H. de O. Fonseca, Christopher Averill, Syed A. Rizvi, Matteo Rosati, James L. Cross, Prateek Mittal, Emanuele Zappala, Daniel Levine, \textbf{Rahul M. Dhodapkar}, Chadi G. Abdallah, David van Dijk. {\it BrainLM: A foundation model for brain activity recordings.} Proceedings of the International Conference on Learning Representations. https://doi.org/10.1101/2023.09.12.557460 \\
\multicolumn{2}{c}{} \\

\textit{\textsc{Nov} 2023}& Dong M, Wang B, Wei J, Fonseca A, Perry C, Ouerghi F, Foxman EF$\dag$, Ishizuka JJ$\dag$, {\bf Dhodapkar RM}$\dag$, van Dijk D$\dag$. {\it Causal identification of single-cell experimental perturbation effects with CINEMA-OT.} Nature Methods. \\
\multicolumn{2}{c}{} \\
\textit{\textsc{Sep} 2023}& Klein J*, Wood J*, Jaycox J*, {\bf Dhodapkar RM}*, Lu P*, Gelhausen JR*, Tabachnikova A*, Greene K, Tabacof L, Malik AA, Monteiro VS, Silva J, Kamath K, Zhang M, Dahl A, Ott I, Valle G, Pena-Hernandez M, Mao T, Bhattacharjee B, Takahashi T, Lucas C, Song E, Mccarthy D, Breyman E, Tosto-Mancuso J, Dai Y, Perotti E, Akduman K, Tzeng TJ, Xu L, Geraghty AC, Monje M, Yildirim I, Shon J, Medzhitov R, Lutchmansingh D, Possick J, Kaminski N, Omer SB, Krumholz HM, Guan L, Dela Cruz CS, van Dijk D$\dag$, Ring AM$\dag$, Putrino D$\dag$, Iwasaki A$\dag$. {\it Distinguishing features of Long COVID identified through immune profiling.} Nature. \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{May} 2023}& Kuchroo M, DiStasio M, Song E, Calapkulu E, Zhang L, Ige M, Sheth AH, Majdoubi A, Menon M, Tong A, Godavarthi A, Xing Y, Gigante S, Steach H, Huang J, Huguet G, Narain J, You K, Mourgkos G, {\bf Dhodapkar RM}, Hirn MJ, Bastian R, Wolf G, Krishnaswamy S$\dag$, Hafler BP$\dag$. {\it Single-cell analysis reveals inflammatory interactions driving macular degeneration.} Nature Communications. 2023 Mar 5. \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Mar} 2023}& Ascunce K, {\bf Dhodapkar RM}, Huang D, Hafler BP. {\it Innate immune biology in age-related macular degeneration.} Frontiers in Cell and Developmental Biology. 2023;11.
 \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Mar} 2023}& {\bf Dhodapkar RM}, Jin A, Liu J. {\it Acute Pain Management Protocol for Ophthalmic Procedures.} In First Aid Perioperative Ultrasound: Acute Pain Manual for Surgical Procedures 2023 Mar 3 (pp. 291-311). Cham: Springer International Publishing.
 \\
\multicolumn{2}{c}{} \\
\textit{\textsc{Jan} 2023}& {\bf Dhodapkar RM}, Spadaro JZ, Heng JS, Sinard JH, Lee YH, Habib LA, Pointdujour-Lim R. {\it NK/T-cell Lymphoma With Orbital Involvement: A Case Report and Systematic Review of the Literature.} Ophthalmic Plastic \& Reconstructive Surgery. 2023 Jan 24:10-97.
 \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Sep} 2022}& {\bf Dhodapkar RM}, Spadaro JZ, Adelman RA. A case of extrafoveal focal choroidal excavation. American Journal of Ophthalmology Case Reports. 2022 Sep 1;27:101682. \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Aug 2022}}& {\bf Dhodapkar RM}, Li E, Nwanyanwu K, Adelman R, Krishnaswamy S, Wang JC. {\it Deep learning for quality assessment of optical coherence tomography angiography images.} Scientific Reports. 2022 Aug 12;12(1):13775. \\
\multicolumn{2}{c}{} \\
 \textsc{May} 2022 & {\bf Dhodapkar RM}, Martell D, Hafler BP. {\it Glial-mediated neuroinflammatory mechanisms in age-related macular degeneration.} Seminars in Immunopathology 2022 May 5;doi: 10.1007/s00281-022-00939-3. Epub ahead of print. \\
\multicolumn{2}{c}{} \\
 \textsc{May} 2020 & {\bf Dhodapkar RM} {\it A survey-wide association study to identify youth-specific correlates of major depressive episodes.} PloS One. 2020 May 8;15(5):e0232373. \\
\multicolumn{2}{c}{} \\
 \textsc{Oct} 2017 & Santolucito M, Zhai E, {\bf Dhodapkar RM}, Shim A, and Piskac R. 2017. {\it Synthesizing Configuration
File Specifications with Association Rule Learning.} Proc. ACM Program. Lang. 1, OOPSLA, Article 64
(October 2017), 20 pages. https://doi.org/10.1145/3133888 \\
\multicolumn{2}{c}{} \\
 \textsc{Jun} 2011 & Sanders SJ, Ercan-Sencicek AG, Hus V, Luo R, Murtha MT, Moreno-De-Luca D, Chu SH, Moreau MP, Gupta AR, Thomson SA, Mason CE, Bilguvar K, Celestino-Soper PB, Choi M, Crawford EL, Davis L, Wright NR, {\bf Dhodapkar RM}, ..., State MW. {\it Multiple recurrent de novo CNVs, including duplications of the 7q11.23 Williams syndrome region, are strongly associated with autism.} Neuron. 2011 Jun 9;70(5):863-85. doi: 10.1016/j.neuron.2011.05.002. 
\end{longtable}

\section{Preprints}
Contributions bolded; {\bf *} indicates co-first author, {\bf $\dag$} indicates co-corresponding author. 

\begin{tabular}{rp{11cm}}
 \textit{\textsc{Mar} 2024}& Julio Silva, Takehiro Takahashi, Jamie Wood, Peiwen Lu, Alexandra Tabachnikova, Jeff R Gehlhausen, Kerrie Greene, Bornali Bhattacharjee, Valter Silva Monteiro, Carolina Lucas, \textbf{Rahul M Dhodapkar}, Laura Tabacof, Mario Peña-Hernandez, Kathy Kamath, Tianyang Mao, Dayna Mccarthy, Ruslan Medzhitov, David van Dijk, Harlan M Krumholz, Leying Guan, David Putrino, Akiko Iwasaki {\it Sex differences in symptomatology and immune profiles of Long COVID.} medRxiv preprint medRxiv:2024.02. 29.24303568. 2024 Mar 4.
 \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Jan} 2023}& {\bf Dhodapkar RM.} {\it A deep generative model of the SARS-CoV-2 spike protein predicts future variants.} bioRxiv. 2023:2023-01. \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Oct} 2022}& Rizvi SA, Nguyen N, Lyu H, Christensen B, Caro JO, Zappala E, Brbic M, {\bf Dhodapkar RM*}, Dijk DV.* {\it AMPNet: Attention as Message Passing for Graph Neural Networks.} arXiv preprint arXiv:2210.09475. 2022 Oct 17.
 \\
\multicolumn{2}{c}{} \\
 \textit{\textsc{Sep} 2022}& {\bf Dhodapkar RM.} {\it Representing cells as sentences enables natural-language processing for single-cell transcriptomics.} bioRxiv. 2022:2022-09.
 \\
\multicolumn{2}{c}{}
\end{tabular}

\newpage
%Section: Speaking
\section{Talks}
Contributions bolded; {\bf *} indicates co-first author, {\bf $\dag$} indicates co-corresponding author. 

\begin{tabular}{rp{11cm}}

 \textsc{May} 2022 & Cross-species single-cell transcriptomic analysis reveals factors limiting Müller glia-mediated regeneration in humans. {\bf Dhodapkar RM}, Martell D, Calapkulu E, Xing Y, Zhang L, Menon M, Jin A, Dong AJ, Hafler BP \\
 								 & The Association for Research in Vision and Ophthalmology (ARVO) Annual Meeting \\
 								 & Denver, CO, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{Apr} 2022 & Cross-species single-cell transcriptomic analysis reveals factors limiting Müller glia-mediated regeneration in humans. {\bf Dhodapkar RM}, Martell D, Calapkulu E, Xing Y, Zhang L, Menon M, Jin A, Dong AJ, Hafler BP\\
 								 & Keystone Symposium for Single Cell Biology \\
 								 & Florence, Italy  \\
 \multicolumn{2}{c}{} \\
 \textsc{Nov} 2019 & Identifying adolescent-specific risk factors of major depressive events: a survey-wide association study. {\bf Dhodapkar RM} \\
 								 & Klingenstein Third Generation Foundation National Medical Student Conference \\
 								 & Palo Alto, CA, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{Mar} 2018 & Association between variants in HRG and SERPINA10 with male gender in patients with venous thromboembolism.
 {\bf Dhodapkar RM},  Dykas DJ,  Ma D,  Lee AI \\
 								 & Thrombosis and Hemostatis Societies of North America Summit \\
 								 & San Diego, CA, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{Jun} 2017 & Securing Distributed Database Technology \\
 								 & MongoDB World Conference\\
 								 & Chicago, IL, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{Jun} 2016 & Building Asynchronous Microservices \\
 								 & MongoDB World Conference\\
 								 & New York, NY, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{Jun} 2016 & Security in the Age of the Internet\\
 							    &  World Scholars Leadership Conference\\
 							    &  \textsc{Geumgang University}, Nonsan, Republic of Korea \\
\end{tabular}

\newpage
\section{Posters}
Contributions bolded; {\bf *} indicates co-first author, {\bf $\dag$} indicates co-corresponding author.

\begin{tabular}{rp{11cm}}
 \textsc{Sep} 2022 & Natural Killer/T-Cell Lymphoma (NKTL) with Orbital Involvement: Systematic Review of the Literature. {\bf Dhodapkar RM}, Spadaro JA, Heng JS, Sinard JH, Lee YH, Habib LA, Pointdujour-Lim R \\
 								 & American Society of Ophthalmic Plastic and Reconstructive Surgery Fall Scientific Symposium \\
 								 & Chicago, IL, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2022 & Deep learning for quality assessment of optical coherence tomography angiography
images. {\bf Dhodapkar RM}, Li E, Nwanyanwu K, Adelman RA, Krishnaswamy S, Wang JC \\
 								 & Symposium on Artificial Intelligence for Learning Health Systems \\
 								 & Bermuda  \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2022 & Deep learning for quality assessment of optical coherence tomography angiography
images. Wang JC, {\bf Dhodapkar RM}, Li E, Nwanyanwu K, Adelman RA, Krishnaswamy S\\
 								 & The Association for Research in Vision and Ophthalmology (ARVO) Annual Meeting \\
 								 & Denver, CO, USA  \\
 \multicolumn{2}{c}{} \\

 \textsc{May} 2022 & A case of IgLON5 encephalitis with ophthalmoplegia. {\bf Dhodapkar RM}, Kohli AA, Megalla M. \\
 								 & North American Neuro-Ophthalmology Society (NANOS) Annual Meeting \\
 								 & Austin, TX, USA  \\
 \multicolumn{2}{c}{} \\
 \textsc{Nov} 2020 & Is it OK to drive home after an epidural steroid injection? {\bf Dhodapkar RM}, Rajput K \\
 								 & American Society of Regional Anesthesia Pain Medicine Meeting \\
 								 & Virtual (per COVID-19)  \\ 
 \multicolumn{2}{c}{} \\
 \textsc{Nov} 2018 & Whole Exome Sequencing and Extended Thrombophilia Testing in Patients with Venous Thromboembolism.  Shevell LM, Lee E, MD, {\bf Dhodpkar RM} Dykas D, Popa A, Ma D, Bar N, Baluha A, Burns A, Chaar C, Dupont A, Gu S, Halene S, Luciano R, Marien R, Neparidze N, Parker T, Yao X, Camire R, Ebberink E, Garcia de Frutos P, Gnanasambandan K, Sayeski PP, Huntington JA, Lentz SR, Mertens K, Parish C, Rezaie R, Connors JM, Leavvitt A, Bale A, Lee, AI \\
 								 & American Society of Hematology Annual Meeting \\
 								 & San Diego, CA, USA\\
\end{tabular}


\section{Other Published Materials}
\begin{tabular}{rp{11cm}}
 \textsc{May} 2022 &  Focal Choroidal Excavation (FCE) {\bf Dhodapkar RM}, Spadaro JZ, Adelman RA. {\it EyeWiki} \\
 \multicolumn{2}{c}{} \\
 \textsc{May} 2022 &  Growth Guidance Instrumentation with Hemivertebra Resection.  Molho D, {\bf Dhodapkar RM}, Bouloussa H, DiLuna M, Tuason D. {\it Pediatric Orthopaedic Society of North America Academy} \\
 \multicolumn{2}{c}{}
\end{tabular}

%Section: Languages
\section{Natural Languages}
\begin{tabular}{rl}
\textsc{Spanish:}&Advanced\\
\textsc{Hindi:}&Basic\\
\textsc{Korean:}&Basic\\
\end{tabular}

\section{Programming and Information Systems}
\begin{tabular}{rl}
\textsc{Languages:}&Python, Perl, JavaScript, Java, C, C++, R\\
\textsc{Expertise:}&Single Cell Genomics, Machine Learning, Information Architecture\\
\textsc{Tools:}&MongoDB, PostgreSQL, Kerberos, LDAP, SAMtools, CUDA
\end{tabular}

\end{document}